---
name: Colton
surname: Baumler
position: "Graduate Student Candidate"
pronouns: He/Him
address: "Data Intensive Biology lab of the University of California, Davis"
#phone: +1 555 555 5555
www: ""
email: "ccbaumler@ucdavis.edu"
twitter: ""
github: ccbaumler
linkedin: colton-baumler
orcid: 0000-0002-5926-7792
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: "9e2e2e"
aboutme: "I am deeply engaged in bioinformatics and mentorship. I excitedly wrangle data, craft software, and create dynamic mentorship opportunities."
docname: awesomecv
output:
  vitae::awesomecv
---

```{r setup, include=FALSE}
# Go to https://yihui.org/tinytex/r/#debugging
# if you experience any latex erros

knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)

require(xfun)

packages <- c('vitae'     # The CV's LaTeX Template
             ,'tibble'    # Data structure for tribbles
             ,'magrittr'  # The Pipe %>%
             ,'here'      # Relative File Paths
             ,'readr'     # Data Loading
             ,'glue'      # String Manipulation
            )

xfun::pkg_attach2(packages, message = FALSE)

source(file = here("data", "data.r"))

```

# Research Interests

 * Bioinformatically exploring the world of big, public data in new and interesting ways.
 * Combining scientific domains to create a pleasant end-user experience.
 * I have overcome many obstacles to be where I am today and I am just happy to be here.

# Education

```{r EDUCATION}

edu %>%
  detailed_entries(
    with = inst,
    what = degree,
    why = detail,
    when = glue::glue("{startYear} - {endMonth} {endYear}",.na = ""),
    where = where
  )

```

# Research Experience

```{r EXPERIENCE}

exp %>%
  detailed_entries(
    with = title,
    what = unit,
    why = detail,
    when = glue::glue("{startMonth} {startYear} - {endMonth} {endYear}",.na = ""),
    where = where
  )

```

\pagebreak

# Professional Service

```{r SERVICE}

service %>%
  detailed_entries(
    with = area,
    what = accomplishment,
    why = detail,
    when = glue::glue("{startYear} - {endYear}{endMonth}",.na = ""),
    where = where
  )

```

# Community Involvement

```{r COMMUNITY}

community %>%
  detailed_entries(
    with = area,
    what = accomplishment,
    why = detail,
    when = glue::glue("{startYear} - {endYear}{endMonth}",.na = ""),
    where = where
  )

```

# Funding and Grants

```{r FUNDS}

funds %>%
  detailed_entries(
    with = area,
    what = accomplishment,
    why = detail,
    when = glue::glue("{startYear} - {endYear}",.na = ""),
    where = where
  )

```

# Honors and Awards

```{r HONORS}

honors %>%
  detailed_entries(
    with = area,
    what = accomplishment,
    why = detail,
    when = glue::glue("{month} {year}",.na = ""),
    where = where
  )

```

# Skills

```{r SKILLS}

skills %>%
  detailed_entries(
    with = area,
    what = skills
  )

```

# Presentations

```{r PRESENTS}

presents %>%
  detailed_entries(
    with = area,
    what = accomplishment,
    why = detail,
    when = year,
    where = where
  )

```
